Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
extended the 'describing aircraft EPS' section

@@

[TODO: 4-line pseudo-code for how we apply priority tables]

>>>>

In this paper, we discuss \emph{load management systems (LMS)} that encompass the GCU and BPCU responsibilities such as load shedding and the assignment of generators to buses. 
The load shedding and generator assignments are actuated by the contactors, though we focus on the high-level control and assume there is an interface to convert our control instructions to contactor configurations.

Also, most of the examples in this paper use a system with the following configuration.
Each side of the aircraft has a bus, and the left-side and right-side buses each have a set of sheddable and nonsheddable tasks.
There are three generators--Generator 1 is part of the left-side engine, Generator 2 is part of the right-side engine, and the auxiliary power unit (APU) is generally used only when one or both of the main generators has failed.

@@

%[TODO: 4-line pseudo-code for how we apply priority tables]
